---
title: " BCN traffic accident explorer"
author: "David Contreras Carretero"
date: "16/4/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(kableExtra)
```

## Barcelona's traffic accident explorer

 Shiny app that allows to explore Barcelona city traffic accidents through an interactive map.
 Main features are:
 
- Data download from Barcelona's open data service. 
- Interactive map, alows to navigate, filter and select data in user drawn polygon. 
- Summary of selected data, selected data is summarized showing daily average.
- Plots showing distribion by week day, hour range and typology of accident. 
- Data grid showing selected data.  


## Original Data

```{r message=FALSE, warning= FALSE}

url2020 <-  "https://opendata-ajuntament.barcelona.cat/data/dataset/834b8920-0685-4e16-8e20-faf13645f4f3/resource/86a3b39c-3cbc-4efd-977a-92ec9cb1b48a/download/2020_accidents_tipus_gu_bcn.csv"

file2020 <- "../data/2020_accidents_tipus_gu_bcn.csv"

#download.file(url2020,file2020)
data <- read.csv(file2020, encoding="UTF-8", sep = ";")


```
As you can see original data is posted in catalan, both values and column names. After a good thinking on the matter I decided to
translate it to English to do this exercise. 



## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

